---
title: "Natalia's Third Space Report"
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: tango
    theme: paper
    fig_caption: yes
    number_sections: no
  blastula::blastula_email: default
---

# Set-Up

```{r setup, message=FALSE, warning=FALSE}
# packages:
library(natalia) #custom
library(knitr) #core
library(tidyverse) #core
library(lubridate) #datetimes
library(ical) #calendar
library(glue) #messages
library(vcd) #mosaic
library(janitor) #tables
library(targets) #caching

# options:
opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

# goal:
goal <- 36
```

```{targets class_types, tar_simple = TRUE}
read_csv("data/class_types.csv")
```

```{targets classes_attended, tar_simple = TRUE}
## classes attended
# TODO, cache the connection results in case cannot open connection
my_url <- paste0(
  "https://thirdspace.fisikal.com/calendar.ics?auth_token=",
  Sys.getenv("THIRDSPACE_KEY")
)
ical_parse_df(my_url) %>%
  tibble() %>%
  filter(uid != "447920804763") %>%
  mutate(
    Length = end - start,
    Class = trimws(str_remove(summary, " at Canary Wharf")),
    Trainer = str_remove(description, "Trainer: "),
    # Date-time vars:
    week_number = isoweek(start),
    week_day = wday(start, label = TRUE, week_start = 1),
    time_type = case_when(
      am(start) == TRUE ~ "Morning",
      hour(start) >= 12 & hour(start) <= 16 ~ "Afternoon",
      pm(start) == TRUE ~ "Evening"
    ) %>%
      factor(
        levels = c("Morning", "Afternoon", "Evening"),
        ordered = TRUE
      )
  ) %>% 
  left_join(class_types, by = c("Class" = "class_title"))
```

```{r}
# tar_make()
# tar_load(classes_attended)
```


```{r, eval=FALSE}
# Step           Cycle Problem!
# Metaburn!! also problem
classes_attended2 <- classes_attended 
  # natalia::fuzzy_join(class_types, by = c("Class" = "class_title"), useBytes = F, max.distance = .1) %>%
  # left_join(class_types, by = c("JOIN" = "class_title")) %>% select(-JOIN)
# check
classes_attended2 %>%
  select(Class, class_type) %>%
  unique() %>%
  arrange(class_type)
```


Value Aim: between £5 and £9 per class (i.e., 36-20 classes per month).


# Analysis
## This Month Analysis

Value extracted so far:

```{r}
this_month <- classes_attended %>%
  filter(year(end) == year(today())) %>%
  filter(month(end) == month(today())) %>% 
  filter(end <= now())
glue("Current value this month: £{round(180/nrow(this_month),2)} per class.")
```

How to pace myself to meet my goals:

```{r}
days_left <- ceiling_date(today(), "month") - today() - 1
pace <- (goal - nrow(this_month)) / as.numeric(days_left)
glue(
  "There are {days_left} days left in the month.
  This means the necessary pace is {round(pace, 2)} classes per day for the rest of the month to hit the {goal} classes goal."
)
```

This is how I can meet my aim this month:

```{r}
# y <- function(x) goal - nrow(this_month) - 2 * x
# plot(y, from = 0, to = 10)
x = 0:days_left
y = 0:days_left
z = 0:days_left
expand_grid(x, y, z) %>%
  filter(x + y + z <= days_left) %>%
  filter(x + 2*y + 3*z == goal - nrow(this_month)) %>%
  mutate(non_gym_days = days_left - x - y - z) %>%
  arrange(non_gym_days) %>%
  rename(Single_Class_Days = x, 
         Double_Class_Days = y,
         Triple_Class_Days = z)
```

```{r}
this_month %>% 
    tabyl(week_number, class_type)
```

## This Week Analysis

```{r}
classes_attended2 <- classes_attended %>% filter(end <= now())
```

```{r}
past6days <- classes_attended %>% 
  filter(end <= now() & start >= today() - 6)
out <- past6days %>%
  mutate(date = date(start)) %>%
  # add the missing/ rest days
  tabyl(date, class_type)
tibble(out)
#rest: 7-nrow(out)

past6days$Class
```

2 (Active) Recovery
2 Cardio
3 Strength




## All-Time Analysis
### Value Analysis

```{r, results='asis'}
money_spent <- 180 * length(unique(ceiling_date(classes_attended$start, "month")))
n <- nrow(filter(classes_attended, end <= now()))
glue("Overall value so far: £{round(money_spent/n, 2)} per class.")
# ifelse(money_spent/n >= 9, try better! {red}) 
#<9 && >7 getting there! {yellow}
#<=7 && >=5 good job! {green} 
#<5 Whoa! gym break maybe? {purple}
```

```{r, eval=FALSE}
library(crayon)
green("d")
```

```{r}
classes_attended %>%
  group_by(year(start), month(start, label = T)) %>%
  summarise(n = n()) %>%
  mutate(`Value (£ per class)` = round(180 / n, 2)) %>%
  rename(Month = `month(start, label = T)`, 
         Year = `year(start)`,
         `Classes #` = n)
```

### Other Stats

My most popular classes:

```{r}
quick_summary(classes_attended, Class)
```

```{r}
classes_attended %>%
  ggplot(aes(x = class_type)) +
  geom_bar()
```


```{r}
classes_attended %>% 
  tabyl(week_number, class_type) %>%
  tibble()
# classes_attended %>% group_by(week_number, class_type) %>% count()
```

Weekly:

- Athletic and Rig ~ 2
- Combat ~ 1-3
- Cycle ~ 2
- Dance ~ 1
- Mind & Body ~ 2
- Strength & Conditioning (!!) => 2!
- Yoga ~ 1?

3 days strength (48h inbetween), 2 days cardio, 2 days active recovery (M&B or Yoga)
No more than 2 Hardcore cycle a week


```{r}
day_types <- classes_attended %>% 
  mutate(date = date(start)) %>%
  group_by(date, class_type) %>%
  summarise() %>%
  nest(class_type) %>% 
  mutate(data = flatten(data))
  # tabyl(date, class_type) %>% tibble() %>%
  # nest(data = `Athletic and Rig`:Yoga)
day_types <- day_types %>%
  full_join(tibble(date = seq(min(day_types$date), max(day_types$date), by = "days"))) %>%
  arrange(date) %>%
  mutate(day_type = case_when(
    is.null(data[[1]]) ~ "Rest",
    "Athletic and Rig" %in% data[[1]] ~ "Strength",
    "Strength and Conditioning" %in% data[[1]] ~ "Strength",
    "PT Workshop" %in% data[[1]] ~ "Strength",
    "Swimming" %in% data[[1]] ~ "Cardio",
    "Dance" %in% data[[1]] ~ "Cardio",
    "Cycle" %in% data[[1]] ~ "Cardio",
    "Combat" %in% data[[1]] ~ "Cardio",
    "Mind and Body" %in% data[[1]] ~ "Active Recovery",
    "Yoga" %in% data[[1]] ~ "Active Recovery"
  ))
# day_types %>% filter("Dance" %in% data[[1]])
# day_types %>% filter(str_detect(data, "Dance"))
day_types %>%
  mutate(data = paste0(data[[1]], collapse = ", ")) %>%
  tail(20)
day_types %>%
  filter(date >= today() - 6 & date <= today()) %>%
  quick_summary(day_type)
```


```{r}
quick_summary(classes_attended, Trainer)
```

```{r}
# quick_summary(classes_attended, time_type)
classes_attended %>%
  ggplot(aes(x = time_type)) +
  geom_bar()
hist(hour(classes_attended$start))
```

```{r}
# quick_summary(classes_attended, week_day)
classes_attended %>%
  ggplot(aes(x = week_day)) +
  geom_bar()
```


Classes not yet attended:

```{r}
class_types %>%
  anti_join(classes_attended, by = c("class_title" = "Class")) %>%
  arrange(class_type) %>%
  select(class_type, class_title)
```

